Model Building

### 2020-08-15 KB_modeling.Rmd
Added new dataset of playoff success

dat <- dat %>%
  mutate_at(vars(DivWin, WCWin, LgWin, WSWin), funs(as.logical)) %>%
  mutate(
    playoffs = case_when(
      WSWin ~ "Won WS",
      LgWin ~ "Won League",
      WCWin  ~ "Won Conference",
      DivWin  ~ "Won Division",
      TRUE ~ "Did not qualify"
    ),
    playoffs = forcats::fct_inorder(playoffs),
    phase = case_when(
      month < 04 | month > 10 ~ "Summer",
      month == 04 ~ "Opening",
      month < 10 & month > 04 ~ "Season",
      month == 10 ~ "Playoffs"
    ),
    phase = forcats::fct_reorder(phase, month),
    is_playoffs = as.integer(phase == "Playoffs")
  ) %>%
  mutate_at(vars(month, year, team), funs(factor))

@@

## playoffs variable
#  Did Not make Playoffs or WC Play-in 
#  Played in WC Play-In
#  Eliminated Round 1
#  Eliminated Round 2
#  Lost WS
#  Won WS
```

>>>>

## Added new dataset for playoff
playoff_success <- read.csv("MLB_Postseason_Success.csv")

dat <- dat %>%
  # mutate_at(vars(DivWin, WCWin, LgWin, WSWin), funs(as.logical)) %>%
  mutate(
  #   playoffs = case_when(
  #     WSWin ~ "Won WS",
  #     LgWin ~ "Lost WS",
  #     WCWin  ~ "Won Wild Card",
  #     DivWin  ~ "Won Division",
  #     TRUE ~ "No Playoffs"
  #   ),
    # playoffs = forcats::fct_inorder(playoffs),
    phase = case_when(
      month < 04 | month > 10 ~ "Summer",
      month == 04 ~ "Opening",
      month < 10 & month > 04 ~ "Season",
      month == 10 ~ "Playoffs"
    ),
    phase = forcats::fct_reorder(phase, month),
    # is_playoffs = as.integer(phase == "Playoffs")
  ) %>%
  mutate_at(vars(month, year, team), funs(factor))

@@

## playoffs variable
#  Did Not make Playoffs or WC Play-in
#  Played in WC Play-In - Going to need to look up and manually add (Is this only the team that lost the wild card?)
#  Eliminated Round 1 - Going to need to look up and manually add
#  Eliminated Round 2 - Going to need to look up and manually add
#  Lost WS - LgWin but no WSwin
#  Won WS - WSWin 
```

### 2020-08-15 Model_Build.Rmd
Added new dataset of playoff success

## Hierarchial Model
```{r}
# all I did was add propTVMarketSize as a key when converting to tsibble, not sure if that's the correct way to do it? I didn't add propTVMarketSize to the arima model.  It says it wasn't found if I add it there.

>>>>

## Hierarchial Model (Note Right)
```{r}
# all I did was add propTVMarketSize as a key when converting to tsibble, not sure if that's the correct way to do it? I didn't add propTVMarketSize to the arima model.  It says it wasn't found if I add it there.
